---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This package provides SOFT-IMPUTE algorithm, proposed by Dr.Robert Tibshirani et al, for the nuclear norm regularized least-squares problem that scales to large problems. Iteratively, this algorithm replaces the missing elements with those obtained from a soft-thresholded SVD. At every iteration this method decreases the value of the objective function towards its minimum, and at the same time gets closer to the set of optimal solutions of the problem. 

## Description

This package only contains 1 function, AdmmMC. This function can be used to complete large low rank matrix with missing elements.

3.1 Parameters:
#### x: The matrix with missing value of your interest. Please transform to matrix if not, e.g. as.matrix()
#### iniMatrix: The matrix with your initial guess replacing the missing value. If no input for this parameter, the function will use 1/2(min+max) as the initial value for all the missing elements in the matrix
#### error: The error you can stand for convergence. The default setting is 1e-16
#### lambda: Regularization parameter controlling the nuclear norm of the minimizer Z. The default setting is 0.5
#### silence: The function will automatically show step number and objective function value after each iteration. Please change to "F" if you don't want to track each iteration

3.2 Return: The function will return a matrix with same dimention as your matrix of interest. All the missing values will be replaced by the elements of the estimated Z in last iteration


## Example

The testing dataset is a incomplete matrix from the famous Mona Lisa picture (jpg). Twenty percent of elements are randomly selected and deleted. The incomplete matrix is saved as an external data in the package in a form of dataframe, named mona. The matrix with missing values is plotted and unfortunately Mona Lisa is not smilling!!!

```{r}
library(jpeg)
library(gplots)
library(MC6068)
data(mona,package="MC6068")
heatmap.2(as.matrix(mona), Rowv = NA, 
          Colv = NA, key = F, scale = "none", 
          col = grey.colors,
          trace = "none",
          labRow = "", labCol = "")
```

The incomplete matrix will be completed by AdmmMC function. The function is muted by changing silence argument to "F". The completed matrix is plotted and Mona Lisa is smilling again!

```{r}
SmileAgain <- AdmmMC(x=as.matrix(mona), silence=T)
heatmap.2(SmileAgain, Rowv = NA, 
          Colv = NA, key = F, scale = "none", 
          col = grey.colors,
          trace = "none",
          labRow = "", labCol = "")
```
